# Simulation helpers

## Helper to parse arguments from the command line

We'll define a function called `parse_args()` to parse trailing arguments to `Rscript`. Let's say we ran something like  this:

```{sh, eval = FALSE}
Rscript gradients.R\
	gradients_num=1\
	arraynum=$SLURM_ARRAY_TASK_ID\
	arraynum_max=$SLURM_ARRAY_TASK_MAX\
	summ=1
exit 0
```
Then, the R script `gradients.R` can include this:

`parse_args(args = commandArgs(trailingOnly = TRUE), verbose=TRUE)`

to have access to the arguments `gradients_num`, `arraynum`, `arraynum_max`, and `summ`.


```{r}
#' Parse command line arguments and assigns the values of them. |args| is meant
#' to just be additional command line arguments.
#'
#' @param args Argument.
#' @param verbose Whether to be loud
#'
#' @examples \dontrun{parse_args(args = commandArgs(trailingOnly = TRUE))}
#'
#' @export
parse_args <- function(args, verbose=FALSE){
  args = sapply(args, strsplit, "=")
  print(args)
  for(arg in args){

    ## Check if the thing is integer
    all_numbers = stringr::str_detect(arg[2], "^[:digit:]+$")
    print(all_numbers)

    ## Assign the variable
    if(all_numbers){
      assign(arg[1], as.numeric(arg[2]), inherits = TRUE)
    } else {
      assign(arg[1], arg[2], inherits = TRUE)
    }

    if(verbose){
      cat(arg[1], "takes the value of", arg[2],
          "from command line input", fill=TRUE)
    }
    print("===============================")
  }
}
```


## Helper to create a folder if it doesn't exist.


```{r}
#' Creates a directory \code{destin}, if it doesn't already exist.
#'
#' @param destin Destination directory.
#'
#' @export
create_destin <- function(destin){
  if(!dir.exists(destin)){
    dir.create(destin, recursive = TRUE)
    cat("Creating destin: ", destin, fill=TRUE)
  } else {
    cat("All output goes out to destin: ", destin, fill = TRUE)
  }
}

```

## Helper to divide jobs into 'chunks'

Take a long matrix `iimat` whose rows encode the configuration of jobs you want
to run. 

For instance, `flowmix::make_iimat()` makes a long matrix whose rows look like this:

```{}
#' ind ialpha ibeta ifold irep
#'  55      6     1     2    1
#'  56      7     1     2    1
#'  57      1     2     2    1
#'  58      2     2     2    1
#'  59      3     2     2    1
#'  60      4     2     2    1
```
And `flowtrend::make_iimat()` makes a matrix whose rows look like this:

```{}
#' ind    iprob  imu ifold irestart
#'  55      6     1     2    1 
#'  56      7     1     2    1
#'  57      1     2     2    1
#'  58      2     2     2    1
#'  59      3     2     2    1
#'  60      4     2     2    1
```

The helper function `make_iilist()` will help you divide this into
`arraynum_max` jobs. This is useful if you are running many pre-defined jobs and
want SLURM to help you get `arraynum_max==100` cores to run these jobs.

```{r}
#' Helper to divide up the jobs in \code{iimat} into a total of
#' \code{arraynum_max} jobs. The purpose is to divide the jobs, in order to run
#' this on a server.
#'
#' @param arraynum_max Maximum SLURM array number.
#' @param iimat matrix whose rows contain CV job indices.
#'
#' @export
make_iilist <- function(arraynum_max, iimat){
  iimax = nrow(iimat)
  if(arraynum_max > iimax){
    iilist = lapply(1:iimax, function(a)a)
  } else {
    ends = round(seq(from=0, to=iimax, length=arraynum_max+1))
    iilist = Map(function(a,b){ (a+1):b}, ends[-length(ends)], ends[-1])
    stopifnot(length(unlist(iilist)) == nrow(iimat))
  }
  stopifnot(length(unlist(iilist)) == nrow(iimat))
  stopifnot(all(sort(unique(unlist(iilist))) == sort(unlist(iilist))))
  return(iilist)
}

```
